Invariant Representations for Noisy Speech Recognition

### 2016-11-30 paper.tex
Itemize gradient reverse and network architecture sections

\section{Experiments}
\label{sec:experiments}
We experimentally evaluate our approach   
on the well-benchmarked Aurora-4 \citep{parihar2002aurora} noisy speech recognition task. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which was added to clean data. Every clean and noisy utterance is filtered to simulate the frequency characteristics %%% of the sampling frequency. ?????  don;t follow % bhuv 
% Dima: is it correct now?
%
The training
data  contains 4400 clean utterances and 446 utterances for each noise condition,
i.e. a total of 2676 noisy utterances.
The test set consists of clean data, data corrupted by 6 noise types, and data recorded with a different microphone for both clean and noisy cases.

@@

    %{\bf We need to make the message of this paragraph more clear.}
    % Dima: tried to fix -- it is differnt => needs more investigation

>>>>

\section{Experiments}
\label{sec:experiments}
We experimentally evaluate our approach   
on the well-benchmarked Aurora-4 \citep{parihar2002aurora} noisy speech recognition task. Aurora-4
is based on the Wall Street Journal corpus (WSJ0). It contains noises of 
six categories which was added to clean data. Every clean and noisy utterance is filtered to simulate the frequency characteristics.The training
data  contains 4400 clean utterances and 446 utterances for each noise condition,
i.e. a total of 2676 noisy utterances.
The test set consists of clean data, data corrupted by 6 noise types, and data recorded with a different microphone for both clean and noisy cases.

@@

### 2016-11-30 poster.tex
Itemize gradient reverse and network architecture sections

\begin{block}{Generative Adversarial Networks}
    \begin{itemize}
        \item The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a sample, e.g. an image, 
    similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``fake'' generated image and the ``real'' image taken from the dataset~\cite{goodfellow2014generative}. 
    \begin{align*}
        \min_G \max_D V(D, G) =& \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            &\mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

@@

    \begin{block}{Domain Adaptation with Reverse Gradient}
        \begin{itemize}
    \item 
    Prior work by~\cite{ganin2014unsupervised} proposed a method of training a network 
    which can be adapted to new domains. The training data consists of the images
    labeled with classes of interest and separate domain (image background) labels. 
    %For example, the domain may refer to image background. The testing set does not need
   % to have the domain labels. 
    The network has a $Y$-like structure: the image is fed to the
    first network which produces a hidden representation $h$. Then this representation $h$ is input to two separate networks: a domain classifier network (D) and 
    a target classifier network (R). The goal of training is to learn the hidden 
    representation that is invariant to the domain labels and performs well on the target classification task, so that the domain information doesn't 
    interfere with the target classifier at test time. Similar to the GAN objective, which forces the generation distribution be close to the data distribution,
    the \emph{gradient reverse method} makes domain distributions similar to each other.

@@

        \begin{column}{\onecolwid} % The second column
            \begin{block}{{\Large Invariant Representation Network}}
                \begin{itemize}
                    \item The model consists of three neural networks. The encoder $E$ produces
                        the intermediate representation $h$ which used in the recognizer $R$ and 
                        in the domain discriminator $D$. The hidden representation $h$ is trained to improve
                        the recognition and minimize the domain discriminator accuracy. The domain discriminator
                        is a classifier trained to maximize its accuracy on the noise type
                        classification task.
                \end{itemize}
                \begin{equation*}
                    L = L_1(\hat{y}, y; \theta_R, \theta_E) + 
                    \alpha L_2(\hat{d}, d; \theta_D) -
                    \beta L_3(\hat{d}, d; \theta_E)
                \end{equation*}

@@

                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. Bottom: Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}

@@

        \item Future research includes enhancements to the domain adaptation network while exploring 
            alternative network architectures and invariance-promoting loss functions.
    \end{itemize}
\end{block}
%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------
\begin{block}{References}
    \bibliographystyle{amsalpha}
    \bibliography{refs.bib}
\end{block}
%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

>>>>

\begin{block}{Generative Adversarial Networks}
    \begin{itemize}
        \item Two networks: the generator and the discriminator.
        \item The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a sample, e.g. an image, 
    similar to the images in the training set.

        \item The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``fake'' generated image and the ``real'' image taken from the dataset~\cite{goodfellow2014generative}. 
    \begin{align*}
        \min_G \max_D V(D, G) = & \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            & \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

@@

    \begin{block}{Domain Adaptation with Reverse Gradient}
        \begin{itemize}
            \item 
            Prior work by~\cite{ganin2014unsupervised} proposed a method of training a network 
            which can be adapted to new domains.

            \item $Y$-like network: the image is fed to the
            encoder network ($E$) which produces a hidden representation $h$.

            \item This representation $h$ is input to two separate networks: a domain classifier network ($D$) and 
            a target classifier network ($R$).

            \item The goal of training is to learn the hidden 
            representation that is invariant to the domain labels and performs well on the target classification 
            task.

            \item Similar to the GAN objective, which forces the generation distribution be close to the data distribution,
            the \emph{gradient reverse method} makes domain distributions similar to each other.
        \end{itemize}

@@

        \begin{column}{\onecolwid} % The second column
            \begin{block}{{\Large Invariant Representation Network}}
                \begin{itemize}
                    \item The model consists of three neural networks. 
                    \item The encoder $E$ produces
                        the intermediate representation $h$ which used in the recognizer $R$ and 
                        in the domain discriminator $D$. 
                    \item The hidden representation $h$ is trained to improve
                        the recognition and minimize the domain discriminator performance. 
                    \item The domain discriminator
                        is a classifier trained to maximize its accuracy on the noise type
                        classification task.
                \end{itemize}
                \begin{equation*}
                    L = L_1(\hat{y}, y; \theta_R, \theta_E) + 
                    \alpha L_2(\hat{d}, d; \theta_D) -
                    \beta L_3(\hat{d}, d; \theta_E)
                \end{equation*}

@@

                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}

@@

        \item Future research includes enhancements to the domain adaptation network while exploring 
            alternative network architectures and invariance-promoting loss functions.
    \end{itemize}
\end{block}
%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------
\begin{block}{Important References}
    \bibliographystyle{amsalpha}
    \bibliography{refs.bib}
\end{block}
%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------
